### 2010-04-09 thesis/SensorMLOnSenseTile/trunk/thesis/SensorMLonSenseTileThesis.tex
latest

\begin{abstract}
This thesis evaluates the use of SensorML and SOS in the development of Sensor Systems. The SenseTile system is used as a case study for this evaluation. A SenseTile web service is developed to access SenseTile sensor data based on a SensorML model of SenseTile. Formalising senor descriptions is also looked using BON to SensorML mapping.

@@

\begin{figure}[h]
\framebox{\scalebox{0.65}{\includegraphics{SMLConceptualModel.png}}}
\caption{SensorML Conceptual Model}\label{fig:SMLConceptualModel}
\end{figure}

@@

\begin{figure}[h]
\framebox{\scalebox{0.65}{\includegraphics{SWESimpleConceptualModel.png}}}
\caption{SWE Common Simple Data Types.}\label{fig:SWESimpleConceptualModel}
\end{figure}

@@

\section{SenseTile}
A case study of the use of SensorML in sensor networks is based on the SenseTile System. SenseTile is a general purpose sensor system developed at UCD CASL \footnote{http://kind.ucd.ie/
products/opensource/SenseTile}. The SenseTile System is used to investigate issues arising with large scale sensor networking. SenseTile is made up of a sensor platform, a datastore, and a compute farm. The below figure shows a outline of this system. 
\begin{figure}[h]
\framebox{\scalebox{0.65}{\includegraphics{SenseTileDescription.png}}}
\caption{SenseTile System}\label{fig:SenseTileDescription}
\end{figure}
 The sensor platform is called the SenseTile Unit and is composed of one or more SenseTile Sensor Boards paired with a SenseTile Processor Unit. The Processor could be a PDA or small PC or any processing device that has a USB connection.  The Sensor Board has a USB connection used for communication with the Processor Unit. There are over a dozen sensors on the SenseTile Sensor Board including a thermistor and light sensor. Sensors are mounted on the Sensor Board and more sensors can be added using the USB connection.

@@

\section{BON}
Business Object Notation (BON) is a method for analysis and design of
object-oriented systems.
seamlessness, reversibility and software contracting.
same same semantic and conceptual base  analysis, design, and implementation by using the
 for the notation on all three levels. It supports source code changes back into design and analysis.
The idea is to treat each subprogram as a subcontractor
who undertakes to deliver some service (specified by a postcondition), but only if
certain prerequisites are fulfilled (the precondition).
same concepts and semantics throughout the development of a
software product allows for a smooth transition from the initial analysis and design models
down to executable code.
\cite{BONref}
\chapter{Design}
\section{Overview}
This chapter describes the design of the SenseTile Web Service. Rather than define any new sensor models or XML formats for SenseTile it preferable to use the existing solutions if good enough for the task at hand. The OGC SWE framework as described in section\ref{SWESec} seems to cover all that is needed for modeling sensors and observations. Central to the design is a SensorML model of the SenseTile System. The section SensorML Model of SenseTile covers the details of this model. This model acts as both metadata about the SenseTile system and provides a description of how to process the sensor data for the SenseTile Web Service.
The Web Service design is based on the SOS specification and allows access to the SensorML model of SenseTile sensors as well as SenseTile sensor observations. Two SOS specification concepts as described in section \ref{SOSSec}, the Data Producer and the SOS itself, structure the design and are described in the SenseTile Web Service section.

@@

\begin{figure}[h]
\framebox{\scalebox{0.65}{\includegraphics{SensorML_SenseTile_System_comp.png}}}
\caption{SenseTile System SensorML Block Diagram}\label{fig:SensorML_SenseTile_System_comp}
\end{figure}

@@

\begin{figure}[h]
\scalebox{0.65}{\includegraphics{Deployment_sensetile.png}}
\caption{SenseTile Web Service}\label{fig:Deployment_sensetile}
\end{figure}

@@

\subsection{Supported Scenarios}
\begin{table}[!th]
\begin{tabular}{|l|c|r|}
\hline
Scenarios\\
\hline
Generate Observations from Sensor Data \\
The DataProducer accesses data from the sensor board \\
\hline
Get Sensor Description from SOS\\
\hline
Get  Sensor Observation from SOS\\
\hline
\end{tabular}
\caption{Scenario Chart for SenseTile Web Service}
\label{ex:table}
\end{table}
\begin{figure}[h]
\framebox{\scalebox{0.65}{\includegraphics{InsertObs.png}}}
\caption{Generate Observation}\label{fig:InsertObs}
\end{figure}

\begin{figure}[h]
\framebox{\scalebox{0.65}{\includegraphics{GetMeta.png}}}
\caption{Find SOS sensor}\label{fig:GetMeta}
\end{figure}

\begin{figure}[h]
\framebox{\scalebox{0.65}{\includegraphics{GetObs.png}}}
\caption{Get Observation from Sensor}\label{fig:GetObs}
\end{figure}
\newpage
\subsection{SenseTile WebService Network Architecture}
\label{subsec:SenseTile WebService Network Architecture}
In the SenseTile Web Service the SOS acts as a gateway to the SenseTile Sensor Network. This prototype is designed with the network architecture as shown in fig \ref{fig:Deployment_network}. A client accesses multiple SOS instances to get observations from the sensor network. An SOS can support several DataProducers and hence would not to be run on every SenseTile Unit.

\begin{figure}[h]
\scalebox{0.65}{\includegraphics{Deployment_sensetile_network.png}}
\caption{SenseTile Sensor Network Architecture}\label{fig:Deployment_network}
\end{figure}
The SOS Specification envisioned that the SOS is run on a large external server as shown in fig \ref{fig:Deployment_ext_sos}. The DataProducers update this external server with observations and SOS Data Consumer access this large SOS.
\begin{figure}[h]
\scalebox{0.65}{\includegraphics{Deployment_sensetile_ext_sos.png}}
\caption{External SOS}\label{fig:Deployment_ext_sos}
\end{figure}

The SOS Specification describes the use of a Proxy SOS as shown in figure \ref{fig:Deployment_sos_aggr}. This architecture could be used with the SenseTile Sensor Network if accessing many SOSs is not feasible for the clients.
\begin{figure}[h]
\scalebox{0.65}{\includegraphics{Deployment_sensetile_sos_aggr.png}}
\caption{Proxy SOS}\label{fig:Deployment_sos_aggr}
\end{figure}

@@

The DataProducer operates by repeating the below steps continously.
 \begin{enumerate}
\item Read Sensor Board Data
\item Process Sensor Data
\item Create O\&M Observations
\end{enumerate}
The steps above are detailed the in following sections with reference
to the BON static diagram \ref{fig:bon_static_diagam_producer.png}.

@@

The UCD SensorBoard Library is used by DataProducer to access
the data generated by the Sensor Board.
The library provides high level interface to the
the data from the sensor board. It reads data from the Sensor board and generates packets
containing the sensor data. These packets provide functionality
to access a particular sensors data such as the temperature
meaurement generated by the thermistor. 
This library is shown as the SensorBoard cluster in \ref{fig:bon_static_diagam_producer.png}
An instance of the class PacketInputStream to is used access the packets from the Sensor Board.

@@

\subsubsection {2. Process Sensor Data}
The PacketInputStream will request the SenseTileSystem to exexcute
the SensorML engine to process the sensor data. The SensoML Enigine
will execute the process chains described in the SenseTile SensorML model.
The sensor objects output will be passed to the coverter objects. The
outputs of both object types are then available to generate observations.

@@

When the SensorML Engine is finished
and there are obsevations generated these
need to be sent to the SOS. An O\&M Onservation
xml string containing the data is sent to
the SOS instance. This is timestamped at
this stage.
 containing the output from
the SensorML processes and send the observations
to the SOS.
-register offerings with the SOS. In this design
each system is an offering.
Need to generate an observation model?

The DataProducer was developed as a SensorML based software. It would be parse the SenseTile SensorML model to instantiate the code to excute the processes described. This required two aspects to be developed, a framework to run the processes and classes that implemented the components.

\begin{figure}[h]
\scalebox{0.65}{\includegraphics{bon_static_diagam_producer.png}}
\caption{DataProducer Static Diagram}\label{fig:bon_static_diagam_producer.png}
\end{figure}

@@

 \begin{figure}[h!]
\scalebox{0.65}{\includegraphics{bon_static_diagam_provider.png}}
\caption{SOS Static Diagram}\label{fig:bon_static_diagam_provider.png}
\end{figure}
The SOS is the main cluster and the Service cluster contains the classes that provide the Web Service interface.

@@

Developing a Web Service is straight forward with Axis2 and it supports several approaches. The supported POJOs (Plain Old Java Objects) approach was used for the SenseTile Web Service as straight forward and the code could be reused on a different framework if AXIS2 did not work well. The Spring framework, which Axis2 supports, was also used for it's dependency injection functionality. A SprinitInit class is needed for Axis to load up the framework.

Axis2 a tool that automatically generates WSDL from the running Web Service. Another tool allows client side code to be generated from the WSDL easing the development of the Web Service clients.

JAXB \footnote{http://java.sun.com/developer/technicalArticles/WebServices/jaxb} was used for SensorML XML to Java binding in the Web Service. JAXB is able to generate a default binding from the complex SWE schema. Some name collisions were corrected with a JAXB customization file found on the SensorML newsgroups.
\section{BON to SensorML mapping}
\lstset{frame=none}
\begin{table}[!th]
\begin{tabular}{|l|r|}
\hline
BON & SensorML\\
\hline
   deferred class AbstractProcess  & not mapped\\
\hline     
     inputs:SEQUENCE[Input] & \begin{lstlisting}
<sml:inputs><sml:inputlist>
SEQUENCE[Input]
<\sml:InputList><\sml:inputs>\end{lstlisting}\\

\hline 
     outputs:SEQUENCE[Output] & not mapped\\
\hline
     parameters:Parameters & not mapped\\

\hline                 
     metaDataGroup:MetaDataGroup & not mapped\\
 \hline

\end{tabular}
\caption{Scenario Chart for SenseTile Web Service}
\label{ex:table}
\end{table}

@@

Developed lighweight Web Service to explore the use of SensorML in Sensor Networks.
running prototype tested with UCD SensorBoard Simulator code.

@@

\chapter{Appendices}
\section{SenseTile SensorML Model}

\lstinputlisting{Thermistor.xml}

\section{BON to SensorML Mapping}
\lstset{basicstyle=\scriptsize,showspaces=false,showstringspaces=false}
\lstinputlisting{SensorML_formal.bon}

\label{endpage}
\end{document}

>>>>

\begin{abstract}
This thesis evaluates the use of SensorML and SOS in the development of Sensor Systems. The SenseTile system is used as a case study for this evaluation. A SenseTile web service is developed to access SenseTile sensor data based on a SensorML model of SenseTile. Formalizing senor descriptions is also looked using BON to SensorML mapping.

@@

\begin{figure}[h]
\centering
\framebox{\scalebox{0.65}{\includegraphics{SMLConceptualModel.png}}}
\caption{SensorML Conceptual Model}\label{fig:SMLConceptualModel}
\end{figure}

@@

\begin{figure}[h]
\centering
\framebox{\scalebox{0.65}{\includegraphics{SWESimpleConceptualModel.png}}}
\caption{SWE Common Simple Data Types.}\label{fig:SWESimpleConceptualModel}
\end{figure}

@@

\section{SenseTile}
A case study of the use of SensorML in sensor networks is based on the SenseTile System. SenseTile is a general purpose sensor system developed at UCD CASL \footnote{http://kind.ucd.ie/
products/opensource/SenseTile}. The SenseTile System is used to investigate issues arising with large scale sensor networking. SenseTile is made up of a sensor platform, a datastore, and a compute farm. The below figure shows a outline of this system. 
\begin{figure}[h]
\centering
\framebox{\scalebox{0.65}{\includegraphics{SenseTileDescription.png}}}
\caption{SenseTile System}\label{fig:SenseTileDescription}
\end{figure}
 The sensor platform is called the SenseTile Unit and is composed of one or more SenseTile Sensor Boards paired with a SenseTile Processor Unit. The Processor could be a PDA or small PC or any processing device that has a USB connection.  The Sensor Board has a USB connection used for communication with the Processor Unit. There are over a dozen sensors on the SenseTile Sensor Board including a thermistor and light sensor. Sensors are mounted on the Sensor Board and more sensors can be added using the USB connection.

@@

\section{BON} \label{BONsec}
Business Object Notation (BON) is a notation and a method for analysis and design of Object-Oriented (OO) systems. It supports a seamless transition from the design to the source code as it based on the same Object Oriented (OO) concepts supported by most OO languages. It is reversible as changes in the source code can be easily mapped back into the design and analysis models. It supports software contracting where each function will guarantee a postcondition specified service if a specified precondition is fulfilled by the caller of the function. BOB support for software contracting allows for a formal description of a system to be developed. For a detailed description of BON see \cite{BONref}.
\chapter{Design}
\section{Overview}
This chapter describes the design of the SenseTile Web Service. Rather than define any new sensor models or XML formats for SenseTile it preferable to use the existing solutions if good enough for the task at hand. The OGC SWE framework as described in section\ref{SWESec} seems to cover all that is needed for modeling sensors and observations. Central to the design is a SensorML model of the SenseTile System. The section SensorML Model of SenseTile covers the details of this model. This model acts as both metadata about the SenseTile system and provides a description of how to process the sensor data for the SenseTile Web Service.
The Web Service design is based on the SOS specification and allows access to the SensorML model of SenseTile sensors as well as SenseTile sensor observations. Two SOS specification concepts as described in section \ref{SOSSec}, the Data Producer and the SOS itself, structure the design and are described in the SenseTile Web Service section.

@@

\begin{figure}[h]
\centering
\framebox{\scalebox{0.65}{\includegraphics{SensorML_SenseTile_System_comp.png}}}
\caption{SenseTile System SensorML Block Diagram}\label{fig:SensorML_SenseTile_System_comp}
\end{figure}

@@

\begin{figure}[h]
\centering
\scalebox{0.65}{\includegraphics{Deployment_sensetile.png}}
\caption{SenseTile Web Service}\label{fig:Deployment_sensetile}
\end{figure}

@@

\subsection{Supported Scenarios}
\begin{table}[!th]
\begin{tabular}{|l|c|r|}
\hline
Scenarios\\
\hline
Generate Observations from Sensor Data \\
The DataProducer accesses data from the sensor board \\
\hline
Get Sensor Description from SOS\\
\hline
Get  Sensor Observation from SOS\\
\hline
\end{tabular}
\caption{Scenario Chart for SenseTile Web Service}
\label{ex:table}
\end{table}
\begin{figure}[h]
\centering
\framebox{\scalebox{0.65}{\includegraphics{InsertObs.png}}}
\caption{Generate Observation}\label{fig:InsertObs}
\end{figure}

\begin{figure}[h]
\centering
\framebox{\scalebox{0.65}{\includegraphics{GetMeta.png}}}
\caption{Find SOS sensor}\label{fig:GetMeta}
\end{figure}

\begin{figure}[h]
\centering
\framebox{\scalebox{0.65}{\includegraphics{GetObs.png}}}
\caption{Get Observation from Sensor}\label{fig:GetObs}
\end{figure}
\newpage
\subsection{SenseTile WebService Network Architecture}
\label{subsec:SenseTile WebService Network Architecture}
In the SenseTile Web Service the SOS acts as a gateway to the SenseTile Sensor Network. This prototype is designed with the network architecture as shown in fig \ref{fig:Deployment_network}. A client accesses multiple SOS instances to get observations from the sensor network. An SOS can support several DataProducers and hence would not to be run on every SenseTile Unit.

\begin{figure}[h]
\scalebox{0.65}{\includegraphics{Deployment_sensetile_network.png}}
\caption{SenseTile Sensor Network Architecture}\label{fig:Deployment_network}
\end{figure}
The SOS Specification envisioned that the SOS is run on a large external server as shown in fig \ref{fig:Deployment_ext_sos}. The DataProducers update this external server with observations and SOS Data Consumer access this large SOS.
\begin{figure}[h]
\centering
\scalebox{0.65}{\includegraphics{Deployment_sensetile_ext_sos.png}}
\caption{External SOS}\label{fig:Deployment_ext_sos}
\end{figure}

The SOS Specification describes the use of a Proxy SOS eeicpr fix. This architecture could be used with the SenseTile Sensor Network if accessing many SOSs is not feasible for the clients.

@@

The DataProducer operates by repeating the below steps continuously.
 \begin{enumerate}
\item Read Sensor Board Data
\item Process Sensor Data
\item Create O\&M Observations
\end{enumerate}
The steps above are detailed the in following sections with reference
to the BON static diagram \ref{fig:bon_static_diagam_producer.png}.

@@

The UCD SensorBoard Library is used by DataProducer to access
the data generated by the Sensor Board.
The library provides high level interface to the
the data from the sensor board. It reads data from the Sensor board and generates packets
containing the sensor data. These packets provide functionality
to access a particular sensors data such as the temperature
measurement generated by the thermistor. 
This library is shown as the SensorBoard cluster in \ref{fig:bon_static_diagam_producer.png}
An instance of the class PacketInputStream to is used access the packets from the Sensor Board.

@@

\subsubsection {2. Process Sensor Data}
The PacketInputStream will request the SenseTileSystem to exexcute
the SensorML engine to process the sensor data. The SensoML Enigine
will execute the process chains described in the SenseTile SensorML model.
The sensor objects output will be passed to the converter objects. The
outputs of both object types are then available to generate observations.

@@

When the SensorML Engine is finished
and there are obsevations generated these
need to be sent to the SOS. An O\&M Onservation
XML string containing the data is sent to
the SOS instance. This is timestamped at
this stage.
 containing the output from
the SensorML processes and send the observations
to the SOS.
-register offerings with the SOS. In this design
each system is an offering.
Need to generate an observation model?

The DataProducer was developed as a SensorML based software. It would be parse the SenseTile SensorML model to instantiate the code to execute the processes described. This required two aspects to be developed, a framework to run the processes and classes that implemented the components.

\begin{figure}[h]
\centering
\scalebox{0.65}{\includegraphics{bon_static_diagam_producer.png}}
\caption{DataProducer Static Diagram}\label{fig:bon_static_diagam_producer.png}
\end{figure}

@@

 \begin{figure}[h!]
\centering
\scalebox{0.65}{\includegraphics{bon_static_diagam_provider.png}}
\caption{SOS Static Diagram}\label{fig:bon_static_diagam_provider.png}
\end{figure}
The SOS is the main cluster and the Service cluster contains the classes that provide the Web Service interface.

@@

Developing a Web Service is straight forward with Axis2 and it supports several approaches. The supported POJOs (Plain Old Java Objects) approach was used for the SenseTile Web Service allowing the code to be reused on a different framework if AXIS2 did not work well. Axis2 supports the The Spring framework which is used in the SenseTile WebService for it's dependency injection functionality. A SprinitInit class is needed for Axis2 to load up the Spring framework.

Axis2 provides a tool that automatically generates WSDL from the running Web Service. Another tool allows client side code to be generated from the WSDL easing the development of the Web Service clients.

JAXB \footnote{http://java.sun.com/developer/technicalArticles/WebServices/jaxb} was used for SensorML XML to Java binding in the Web Service. JAXB is able to generate a default binding from the complex SWE schema. Some name collisions were corrected with a JAXB customization file found on the SensorML newsgroups. However the default binding was not fully successful for the System type. It input, output and parameter properties were missing and the inheritance hierarchy did not provide them. A small change was needed to add these properties and then everything worked fine with marshaling and unmarshaling SensorML Systems.

\chapter{BON to SensorML mapping}
\section{Overview}
In this chapter a BON(see section\ref{BONsec}) to SensorML( see section \ref{SMLsection}) mapping is described. One motivation for this mapping is take advantage of formal software development processes described in \cite{Kiniryref}. This is a verification based process that refines BON to JML and then to Java. Robust software can thus be developed. Another motivation is that it XML is verbose and a more compact description of a SensorML model as facilitated by BON is naturally preferred. Lastly SensorML is complex and it is difficult to develop correct SenorML models based only on using the SensorML XML Schema definition. How a BON specification can help here is described later in the chapter.

\section{SensorML BON Specification}
This sections shows an example of one BON specification to explain the approach used to develop BON specifications for SensorML. The BON specification of SensorML described is very close conceptually to the SensorML model shown in section \ref{SMLsection}. The BON specification developed in this thesis does not address the issue of the SensorML metadata. This information  is for descriptive purposes only and is not used for processing sensor data. BON adds no value here and a different way to add this property  to SensorML sensor descriptions is suggested to be used. One potential way to add this metadata is through the use of XSLT\footnote{http://www.w3.org/TR/xslt20/} but this is not examined further in this thesis.

The listing \ref{BONListing} shows the BON specification for the SensorML AbstractProcess as described in section \ref{SMLsection}.  The AbstractProcess's inputs, outputs and parameters properties are specified as BON features of type SEQUENCE of the appropriate types. These AbstractProcess properties are optional according to the SensorML specification and so there is no postcondition to enforce that a value must be returned. Setter features are provided and also a constructor feature, make, with the most likely used features as the constructor parameters.

The AbstractProcess's metaDataGroup property is not optional in AbstractProcess. In this case the metaDataGroup feature is used a placeholder for the metadata and returns a BON STRING rather than the expected MetaDataGroup.

The complete BON SensorML specification listing can be found in appendix \ref{appenBSMLBONSpec}.
\newpage

 \begin{lstlisting}[basicstyle=\scriptsize,showspaces=false,showstringspaces=false, caption=BON AbstractProcess,label=BONListing]
   deferred class AbstractProcess
     indexing
     about: "base substitution group for all processes.";
     title:        "AbstractProcess.";
     author:       "Ciaran Palmer.";
     copyright:    "none.";
     organisation: "School of Computer Science and Informatics, UCD.";
     date:         "2009/10/29.";
     version:      "Revision: 1.00.";

     feature

     make
       ->inputsIn:SEQUENCE[Input]
       ->outputsIn:SEQUENCE[Output]
       require
         inputsIn/=Void;
         inputsIn/=Void;
       ensure
         delta{inputs,outputs};
         inputs = inputsIn;
         outputs = outputsIn;
       end

     --optional       
     inputs:SEQUENCE[Input]

      --optional        
     outputs:SEQUENCE[Output]

      --optional       
     parameters:Parameters

     metaDataGroup:STRING
        ensure
          Result = "metaDataGroup";
       end

     setInputs
       ->inputsIn:SEQUENCE[Input]
       require
         inputsIn/=Void;
       ensure
         delta{inputs};
         inputs = inputsIn;
       end

      setOutputs
       ->outputsIn:SEQUENCE[Output]
       require
         outputsIn/=Void;
       ensure
         delta{outputs};
         outputs = outputsIn;
       end

      setParameters
       ->ParametersIn:SEQUENCE[Parameter]
       require
         ParametersIn/=Void;
       ensure
         delta{Parameters};
         Parameters = ParametersIn;
       end               
   end --AbstractProcess
 \end{lstlisting}

\section{BON to SensorML Mapping}
Tables of mapping, like table\ref{tab:bonsmlexample} below, are developed to show the mapping of BON features to SensorML XML tags. The mapping is shown from a BON feature to the appropriate SensorML XML tags. The table below shows a mapping for AbstractProcess. The name of the class is not mapped as it is abstract with the sub-classes Component and ProcessModel providing the name of the enclosing tag names. The  BON SEQUENCE types such as SEQUENCE[Input] map to a sequence of Input mapped SensorML XML tags found in the Input mapping table. The full set of tables are in appendix \ref{appenBSMLBONTables}.

\lstset{frame=none}

\begin{table}[!th]

\centering
\begin{tabular}{|l|l|}
\hline
BON features & SensorML XML tags\\
\hline
   deferred class AbstractProcess  & not mapped\\
\hline     
     inputs:SEQUENCE[Input] & \begin{lstlisting}
<sml:inputs><sml:inputlist>
SEQUENCE[Input]
<\sml:InputList><\sml:inputs>\end{lstlisting}\\

\hline 
     outputs:SEQUENCE[Output] & \begin{lstlisting}
<sml:outputs><sml:outputlist>
SEQUENCE[Input]
<\sml:outputList><\sml:outputs>\end{lstlisting}\\
\hline
     parameters:SEQUENCE[Parameter] & \begin{lstlisting}
<sml:parameters><sml:parametertlist>
SEQUENCE[Input]
<\sml:outputList><\sml:outputs>\end{lstlisting}\\

\hline                 
     metaDataGroup:STRING &  \begin{lstlisting}
<\sml:metaDataGroup>metaDataGroup<\sml:metaDataGroup>\end{lstlisting}\\
 \hline

\end{tabular}

\caption{BON to SensorML AbstractProcess Mapping table}
\label{tab:bonsmlexample}
\end{table}

The MetaDataGroup is not described in BON as explained in the overview section. Only a place holder value mapped from this feature.

Connections as described in section x are connected up using strings that have to be parsed to find out the inputs and outputs to connect up. Invariants written in BON can enforce some level of corrects in that inputs in connections must be inputs in the components contained in that chain. This is shown in the BON fragment below.

BON fragment invariant.

SWE and BON Clusters.
\section{BON Thermistor}
Thermistor can be generated by the following BON class.
\section{method}
BON to SensorML
BON to Java\\JML.

@@

Developed lightweight Web Service to explore the use of SensorML in Sensor Networks.
running prototype tested with UCD SensorBoard Simulator code.

@@

\appendix
\chapter{Appendix: SenseTile SensorML Model}
\section{SenseTile SensorML System}
\section{SenseTile SensorML SensorBoardSystem}
\section{SenseTile SensorML ConvetorSystem}
\section{SenseTile SensorML Thermistor}
\lstinputlisting{Thermistor.xml}
\section{SenseTile SensorML CelciusConvertor}

\chapter{Appendix: BON to SensorML Mapping}\label{appenB}
\section {SensorML BON Specifcation}\label{appenBSMLBONSpec}

\lstset{basicstyle=\scriptsize,showspaces=false,showstringspaces=false}
\lstinputlisting{SensorML_formal.bon}
\section {BON to SensorML mapping tables} \label{appenBSMLBONTables}
\lstset{frame=none}
\begin{table}[!th]
\centering
\begin{tabular}{|l|l|}
\hline
BON features & SensorML XML tags\\
\hline
   deferred class AbstractProcess  & not mapped\\
\hline     
     inputs:SEQUENCE[Input] & \begin{lstlisting}
<sml:inputs><sml:inputlist>
SEQUENCE[Input]
<\sml:InputList><\sml:inputs>\end{lstlisting}\\

\hline 
     outputs:SEQUENCE[Output] & \begin{lstlisting}
<sml:outputs><sml:outputlist>
SEQUENCE[Input]
<\sml:outputList><\sml:outputs>\end{lstlisting}\\
\hline
     parameters:SEQUENCE[Parameter] & \begin{lstlisting}
<sml:parameters><sml:parametertlist>
SEQUENCE[Input]
<\sml:outputList><\sml:outputs>\end{lstlisting}\\

\hline                 
     metaDataGroup:MetaDataGroup &  \begin{lstlisting}
<\sml:metaDataGroup><\sml:metaDataGroup>\end{lstlisting}\\
 \hline

\end{tabular}
\caption{BON to SensorML AbstractProcess Mapping table}\label{table:bon_sml_example}
\label{ex:table}
\end{table}
\label{endpage}
\end{document}
